Supplemental Materials, Methods and Results

### 2021-06-01 supp.Rmd
Final fig and final fixes to supp

<!-- ```{r Figcolsig4, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "We presented chameleons with model snake and bird predators to elicit an anti-predator response, particularly, color change, to test the hypothesis that character release in Hawaii would also result in a signal more conspicuous to a predator. (A) A model snake (Dispholidus typus) causing a characteristic contrasting color change and (B) a model bird (Aviceda cuculoides) which was flown over the top of the chameleon."} -->
<!-- figs4 <- image_read("./output/figures/FigS4.png") -->
<!-- figs4 -->

<!-- ``` -->

>>>>

```{r Figcolsig4, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "We presented chameleons with model snake and bird predators to elicit an anti-predator response, particularly, color change, to test the hypothesis that character release in Hawaii would also result in a signal more conspicuous to a predator. (A) A model snake (Dispholidus typus) causing a characteristic contrasting color change and (B) a model bird (Aviceda cuculoides) which was flown over the top of the chameleon."}
figs4 <- image_read("./output/figures/FigS4.jpg")
figs4
